Kindly Bent to Free Us

### 2019-07-08 kindly/motivation.tex
Misc code fixes in the motivations.

\begin{figure}[tp]
  \centering
  \begin{subfigure}[t]{0.48\linewidth}
\begin{lstlisting}
module Array : sig
  type ('a : 'k) t : lin

@@

  val map : (&'a -> 'b) -> &('a t) -> 'b t
end
\end{lstlisting}
    \caption{Affine arrays}
    \label{sig:array}
  \end{subfigure}\hfill
  \begin{subfigure}[t]{0.5\linewidth}
\begin{lstlisting}
let mk_fib_array n =
  let a = create n 1 in
  for i = 2 to n - 1 do
    let x = get (&a, i-1) + get (&a, i-2) in(*@\label{ex:array:get}*)
    set (&!a, i, x)(*@\label{ex:array:set}*)
  done;
  a(*@\label{ex:array:return}*)
# mk_fib_array : int -> int Array.t
\end{lstlisting}
    \caption{Example of use of affine arrays}
    \label{ex:array}
\begin{lstlisting}
let a = create n 1 in
for i = 2 to n - 1 do {|
  let x = {| get &a (i-1) + get &a (i-2) |} in(*@\label{ex:array:region:get}*)
  set &!a i x
|} done;
\end{lstlisting}
    \caption{Excerpt of \cref{ex:array} with explicit regions}
    \label{ex:array:region}
  \end{subfigure}
\end{figure}

@@

\begin{figure}
  \centering
  \begin{minipage}[t]{0.45\linewidth}
    \lstinputlisting[linerange=1-13]{code/sukodu.affe}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.54\linewidth}
    \lstinputlisting[linerange=15-29,firstnumber=last]{code/sukodu.affe}
  \end{minipage}
  \caption{Excerpt of the Sudoku solver}
  \label{ex:sudoku}
\end{figure}

>>>>

\begin{figure}[tp]
  \centering
  \begin{subfigure}[t]{0.47\linewidth}
\begin{lstlisting}
module Array : sig
  type ('a : 'k) t : lin

@@

  val map : (&'a -> 'b) -> &('a t) -> 'b t
end
\end{lstlisting}
    \caption{Affine arrays}
    \label{sig:array}
  \end{subfigure}\hfill
  \begin{subfigure}[t]{0.53\linewidth}
\begin{lstlisting}
let mk_fib_array n =
  let a = create n 1 in
  for i = 2 to n - 1 do
    let x = get (&a, i-1) + get (&a, i-2) in(*@\label{ex:array:get}*)
    set (&!a, i, x)(*@\label{ex:array:set}*)
  done;
  a(*@\label{ex:array:return}*)
# mk_fib_array : int -> int Array.t
\end{lstlisting}
    \caption{Example of use of affine arrays}
    \label{ex:array}
\begin{lstlisting}[firstnumber=2]
  let a = create n 1 in
  for i = 2 to n - 1 do {|
    let x = {| get &a (i-1) + get &a (i-2) |} in(*@\label{ex:array:region:get}*)
    set &!a i x
  |} done;
\end{lstlisting}
    \caption{Excerpt of \cref{ex:array} with explicit regions}
    \label{ex:array:region}
  \end{subfigure}
\end{figure}

@@

\begin{figure}
  \centering
  \begin{minipage}[t]{0.45\linewidth}
    \lstinputlisting[linerange=1-13]{code/sukodu.affe}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.54\linewidth}
    \lstinputlisting[linerange=15-30,firstnumber=last]{code/sukodu.affe}
  \end{minipage}
  \caption{Excerpt of the Sudoku solver}
  \label{ex:sudoku}
\end{figure}
